### 2021-11-09 input/figsimplerproblem.tex
about example

\begin{figure*}
  \newcommand{\SCALE}{0.9}
  \begin{center}
    \subfloat[Part A][\label{fig:problemA}Both $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}Both $a$ and $d$ delete
      their partition while $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}$b$ blocks the only transiting
      $\delta_a$ despite it propagated $\alpha_a$ before.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}$c$ stays in $P_a$ despite it has been deleted.]
             {\input{input/figsimplerproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, naive
    propagation of $\alpha$ and $\delta$ messages is insufficient to
    guarantee consistent partitioning. If $c$ had children, they would
    stay in the wrong partition as well. $c$ must acknowledge
    $P_a$'s \emph{possible} deletion and propagate it.}
\end{figure*}

>>>>

\begin{figure*}
  \newcommand{\SCALE}{0.9}

  \newcommand{\LEFT}{\triangleleft}
  \newcommand{\RIGHT}{\triangleright}

  \begin{center}
    \subfloat[Part A][\label{fig:problemA}(both) $a$ and $c$ become sources.
      $w_{ab} = 2$; $w_{bc} = 1$.]{\input{input/figsimplerproblemA.tex}}
    \hspace{0pt}
    \subfloat[Part B][\label{fig:problemB}(top) $c$ deletes its partition. (bottom)
    $a$ and $c$ delete their partition. (both) $b$ delivers and forwards $\alpha_a$.]
             {\input{input/figsimplerproblemB.tex}}
    \hspace{0pt}
    \subfloat[Part C][\label{fig:problemC}(bottom) $b$ blocks the only transiting
      $\delta_a$ despite it propagated $\alpha_a$ before. (both) $b$ delivers and forwards $\alpha_c$.]
             {\input{input/figsimplerproblemC.tex}}
    \hspace{0pt}
    \subfloat[Part D][\label{fig:problemD}(both) $b$ delivers and forwards $\delta_c$. (top)
    It reaches $a$ that answers with $\alpha_a$. $b$ delivers $\alpha_a$ again. (both) $c$
    stays in $P_a$.]
             {\input{input/figsimplerproblemD.tex}}
  \end{center}
  \caption{\label{fig:problem}Even in the simplest scenarios, naive
    propagation of $\alpha$ and $\delta$ messages may be insufficient
    to guarantee consistent partitioning. In the bottom scenario, if
    $c$ had children, they would stay in the wrong partition
    too. Despite both scenarios look the same from $c$'s perspective,
    $c$ must acknowledge $P_a$'s \emph{possible} deletion and
    propagate it.}
\end{figure*}
